A Container-Based Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-10-16 draft.tex
Proofreading 6.2 refs #20

\subsection{EvoSwarm from the User Point of View} 
\label{sec:evoswarm:config}

@@

After starting the application, users can push several Experiment Definition 
files and start monitoring the current execution in the terminal.
After an experiment is finished, the user must execute another script
that takes as argument the experiment id to generate a collection of files containing all the
data generated by the experiment, again in a JSON format. An example of an 
experiment definition is shown in Listing \ref{code:exp}. We give more details about the 
data contained in the file in the next section. Users can use these files 
to analyze and plot experiment data.  Python
scripts are included in the repository to plot the running times for the
experiments and all other plots used in this paper;  there is also a script to
generate the files needed by the COCO framework \cite{hansen2016coco}, which can generate standard
comparisons against other methods.

>>>>

\subsection{EvoSwarm from the user's point of view} 
\label{sec:evoswarm:config}

@@

After starting the application, users can push several Experiment Definition
files and start monitoring the current execution in the terminal.
After an experiment is finished, the user must execute another script
that takes as argument the experiment id to generate a collection of files containing all the
data generated by the experiment, again in a JSON format. An example of an
experiment definition is shown in Listing \ref{code:exp}. We give more details about the
data contained in the file in the next section. Users can use these files
to analyze and plot experiment data. We include Python
scripts  in the repository to plot the running times for the
experiments and all other charts used in this paper;  there is also a script to
generate the files needed by the COCO framework \cite{hansen2016coco}, which can generate standard
comparisons against other methods.
